### 2017-10-11 Gruba/01-intro.tex
v4.2
v4.2

Central to user behavior modeling, is the need to choose the unit of model (i.e., how many users share one model; for example, the mono model for all users, one model per user, etc), as well as the variety of features to be selected for differentiating these units.
Already, there exist work of building a single model for all the users \refe{}.
Apparently, such model bears the limitation of being coarse.
On the other hand, modeling each user is not practical, due to the tremendous number of users.

The key driver of our work is the realization that in social media applications, users could fall into groups and each group shares representative behaviors.
%
As one example, consider the film \textit{Brave Heart}, fans of which are probably addicted to highland, bagpipe and war films, and thus likely to \ret{} blogs of these topics. 
Particularly, we study the \retg{} behavior of users and our work can be generalized to other behaviors of like and comment as well.
The main challenge is to properly model user groups upon behavior analysis.

>>>>

Central to user behavior modeling, is the need to choose the granularity of model (i.e., how many users share one model), as well as the variety of features to be selected for differentiating these units.
Already, there exist work of building a single model for all the users \cite{IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13,IEEEexample:journals/tkdd/ZhangTLLX15}.
Apparently, such model bears the limitation of being coarse.
On the other hand, modeling each user is not practical, due to the tremendous number of users.

The key driver of our work is the realization that in social media applications, users could fall into groups and each group shares representative behaviors.
%
As one example, consider the film \textit{Brave Heart}, fans of which are probably addicted to highland, bagpipe and war films, and thus likely to \ret{} blogs of these topics.
Particularly, we study the \retg{} behavior of users and our work can be generalized to other behaviors of like and comment as well. 
In the realm of social network behavior research, few work has been done towards making use of grouping, which however has been proved to be effective in other fields.
This motivates us to explore the incorporation of user grouping into the \retg{} behavior modeling, filling the gap of existed studies in literature.

### 2017-10-11 Gruba/02-overview.tex
v4.2
v4.2

We consider people's \retg{} behavior in social media.
For simplicity, with a given user, we assume that blogs created or \retd{} by his/her followees cover the overall candidates, from which the said user may \ret{}.
All our results could straightforwardly generalize to alternative candidate scopes.
%e.g., the like/unlike behavior against the candidate of remarking [double check the network language; register a Facebook]
%e.g., positive comments in the overall comments

\begin{definition}
\label{def:blog}
A blog $B = (O, T, M, R)$ consists of the owner $O$ (a.k.a. user in this paper) to whom $B$ belongs (either created or \retd{}), the timestamp $T$ showing when $B$ is generated, the blog message $M$ and a bit $R$ denoting $B$ is \retd{} (1) or originally created (0) by the owner $O$.
\end{definition}

@@

\begin{definition}
\label{def:user}
A user $U = (B_s, R_s, E_s)$ consists of three sets regarding the user's blogs $B_s$, followers $R_s$ and followees $E_s$ separately.
Each follower/followee per se refers to a user.
\end{definition}

The mapping between blog $B$ and user $U$ is a bilateral operation, i.e., $U = O(B)$ and $B \in B_s(U)$, through ID(s) of user and blog respectively.
%
Informally, providing a set of users $\{U\}$ and the associated blogs $\{B\}$, as well as a blog query $b$ and a follower of $O(b)$ written as $f$, i.e., $f \in R_s(O(b))$, \sys{} shall build a \retg{} model for $(\{U\},\ \{B\})$, upon which Y/N is returned regarding whether $f$ shall \ret{} $b$.

@@

\stitle{Data Storage.} The underlying Data Storage subsystem stores data to be processed by \sys{}, i.e., data of blogs and users, as shown in \textit{Definition} \textit{\ref{def:blog}} and \textit{\ref{def:user}}.

\stitle{Processing Runtime.}
In the heart of \sys{} lies the Processing Runtime subsystem, which consists of three major components as follows.
%\begin{enumerate}

	\stab(1)  Feature Extractor: By coalescing the blog data, each user is depicted by a bunch of features, which are grouped into three categories. They are features of \textit{Info} (e.g., the number of followers and followees), \textit{Behavior} (e.g., the frequency and the popular slots of \retg{}) and \textit{Interest} (e.g., the long-term/recent interests, as well as the explicit/implicit interests). These features are extracted from the stored data by Feature Extractor and serve as the input of User Clusterer.

	\stab(2)  User Clusterer: Providing the user-based features, User Clusterer takes charge of the clustering task such that each user falls into a proper group.

	\stab(3)  Group Modeler: For each group obtained by User Clusterer, Group Modeler employs both positive and negative samples (i.e., blogs that were or weren't \retd{}) to train a model, over which the testing of users' \retg{} behavior is performed.
%\end{enumerate}

>>>>

We consider people's \retg{} behavior in social media.
For simplicity, with a given user, we assume that microblogs created or \retd{} by his/her followees cover the overall candidates, from which the said user may \ret{}.
All our results could straightforwardly generalize to alternative candidate scopes.
%e.g., the like/unlike behavior against the candidate of remarking [double check the network language; register a Facebook]
%e.g., positive comments in the overall comments

\begin{definition}
\label{def:blog}
A microblog $Mb = (O, T, M, flag)$ consists of the owner $O$ (a.k.a. user in this paper) to whom $Mb$ belongs (either created or \retd{}), the timestamp $T$ showing when $Mb$ is generated, the microblog message $M$ and a bit $flag$ denoting $Mb$ is \retd{} (1) or originally created (0) by the owner $O$.
\end{definition}

@@

\begin{definition}
\label{def:user}
A user $u = (B_u, R_u, E_u)$ consists of three sets regarding the user's microblogs $B_u$, followers $R_u$ and followees $E_u$ separately.
Each follower/followee per se refers to a user.
\end{definition}

%The mapping between blog $B$ and user $U$ is a bilateral operation, i.e., $U = O(B)$ and $B \in B_s(U)$, through ID(s) of user and blog respectively.
By Definition \textit{\ref{def:blog}} and \textit{\ref{def:user}}, $u = Mb.O$ and $Mb \in B_u$
%
Informally, providing a set of users $\mathbb{U}$ and the associated microblogs $\mathbb{B}$, as well as a microblog $b$ and a follower of $b.O$ written as $f$, i.e., $f \in R_{b.O}$, \sys{} shall build a \retg{} model for $\mathbb{U}$ and $\mathbb{B}$, upon which 1/0 is returned regarding whether $f$ shall \ret{} $b$.

@@

\stitle{Sina Microblog Data.} It is the data to be processed by \sys{}, i.e., data of microblogs and users, as shown in \textit{Definition} \textit{\ref{def:blog}} and \textit{\ref{def:user}}.

\stitle{Key Modules.}
In the heart of \sys{} lies the Key Modules, which consists of three major components as follows.
%\begin{enumerate}

	\stab(1)  Feature Extraction: By coalescing the microblog data, each user is depicted by a bunch of features, which are grouped into three categories. They are features of \textit{Info} (e.g., the number of followers and followees), \textit{Behavior} (e.g., the frequency and the popular slots of \retg{}) and \textit{Interest} (e.g., the long-term/recent interests, as well as the explicit/implicit interests). These features are extracted from the stored data by Feature Extraction and serve as the input of User Clustering.

	\stab(2)  User Clustering: Providing the user-based features, User Clustering takes charge of the clustering task such that each user falls into a proper group.

	\stab(3)  Group Modeling: For each group obtained by User Clustering, Group Modeling employs both positive and negative samples (i.e., microblogs that were labeled with \retd{} and not \retd{}) to train a model, over which the testing of users' \retg{} behavior is performed.
%\end{enumerate}

### 2017-10-11 Gruba/03-fe.tex
v4.2
v4.2

With the underlying data in Data Storage subsystem, Feature Extractor is responsible for ``mining'' the user characteristics, resulting three features for each user.
These features are \textit{Info Feature}, \textit{Behavior Feature} and \textit{Interest Feature}, which constitute the \textit{Feature Data} in \sys{}, i.e., \textit{Feature Data} = \{\textit{Info Feature}, \textit{Behavior Feature}, \textit{Interest Feature}\}.

@@

\textit{Info Feature} employs a vector $I$ to cover the basic info of user.
\begin{equation}
\label{eq:info}
	I = (\#R_s,\ \#E_s,\ R_{ee},\ \#B_s,\ R_{oc},\ U_t)
\end{equation}
where each variable is illustrated in Table \ref{tbl:fe-info}.
Specifically, we use $\#(B_s | R(B)==1)$ and $\#(B_s | R(B)==0)$ to represent the number of \retd{} blogs and blogs that are originally created by the user.

\begin{table}[!htb]
\centering
\begin{small}
\caption{Illustration of Variables in Info Feature}
\vspace{0.3cm}
\label{tbl:fe-info}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{c}{\textbf{variable}} & \multicolumn{1}{c}{\textbf{illustration}}	\\	\midrule \midrule
\#$R_s$				& number of followers				\\	\midrule
\#$E_s$				& number of followees				\\	\midrule
\multirow{2}{*}{$R_{ee}$}      & \multirow{2}{*}{a ratio defined as $\frac{\#R_s}{\#E_s}$}	\\
 						&                       									\\	\midrule
\#$B_s$				& number of blogs owned by the user				\\	\midrule
\multirow{2}{*}{$R_{oc}$}      & \multirow{2}{*}{a ratio defined as $\frac{\#(B_s | R(B)==1)}{\#(B_s | R(B)==0)}$}	\\
 						&                       									\\	\midrule
$U_t$					& user type (as detailed in Table \ref{tbl:ucate})			\\ \bottomrule
\end{tabular}
\end{small}
\end{table}

@@

Unlike \textit{Info Feature}, \textit{Behavior Feature} shows several statistics regarding the user's \retg{} behavior.
Such statistics include:
\begin{itemize}
	\item a value showing the average number of \retd{} blogs per week: $\#W_r$
	\item a normalized vector regarding the time distribution of a user's \retg{} behavior: $P_t\ = (p'_0,\ p'_1,\ ...,\ p'_{11})$, where $p'_0$ is the probability that the \retg{} activity happens from 0am to 2am, $p'_1$ is the probability that the \retg{} activity happens from 2am to 4am, and so on.
	\item a normalized vector with respect to the gap distribution of a user's \retg{} behavior: $P_g\ = (p''_0,\ p''_1,\ ...,\ p''_{5})$, in which $p''_0$ is the probability that the gap between two \retd{} blogs is within 1 min. Ditto for $p''_1$ (1 min to 1 hour), $p''_2$ (1 to 12 hours), $p''_3$ (12 to 24 hours), $p''_4$ (24 to 48 hours) and  $p''_5$ (more than 48 hours).
\end{itemize}

@@

\begin{definition}
\label{def:bw}
%used \label{def:blog} previously
With a given user $u$, each blog $b \in B_s(u)$ could be decomposed into a set of words $\{w\}$, i.e., $b = \{w\}$.
\end{definition}

@@

In \sys{}, a word, either in the form of $c$ or $w$, acts as the minimum unit for analysis.
Hence, the similarity of a word pair ($w$, $c$), i.e., $sim(w, c)$, could be generalized to the similarity of a blog against one topic $sim(b, t)$, and finally to a user versus each topic in lexicon $sim(u, \{t\})$; topics with similarity satisfying certain thresholds are allocated to the user $u$ and constitute the interests of $u$.

@@

\stitle{Step 1:} Each blog of $u$ is decomposed into a word set, i.e., $b = \{w\}$ where $b \in B_s(u)$.

@@

If $sim(b, t)$ satisfies a certain threshold (3 by default) , topic $t$ is labeled to blog $b$;
the user $u$ is then discovered having an explicit interest (topic) $t$.
Thus, by looking into the similarity of $b$ against all topics in lexicon, the explicit interests of $u$ is returned, in the form of interest feature (see Definition \ref{def:inte}).

@@

\stitle{Step 3:} A metric \textit{TF-IDF weight} $W_f$ is computed, i.e., employing TF-IDF (term-frequency and inverse document-frequency) to calculate the weight distribution of words in blog $b$:
\begin{equation}
\label{eq:tf}
W_f = \{(w_i, p_i)\}
\end{equation}
where $w_i$ refers to a single word, of which the weight is $p_i$, with $\sum_{\substack{i}} p_i = 1$.

To compute such weight $p_i$ for word $w_i$, a metric $p''_i$ is first calculated as:
\begin{equation}
\label{eq:tf-w}
p''_i = \frac{|b_i|}{|b|} * log(\frac{|D_i|}{|D|})
\end{equation}
in which we use the operator $|\ |$ to measure the cardinality, such that $|b_i|$ is the occurrences of word $w_i$ in blog $b$ and $|b|$ the total occurrences of all words in $b$.
Ditto for $|D_i|$ and $|D|$, except that the scope is the overall dataset, rather than a single blog $b$.

@@

\stitle{Step 4:} Similarly, another metric \textit{Twitter-LDA weight} $W_w$ is obtained, i.e., using Twitter-LDA  %\ref{IEEEexample:zhao2011comparing}
\cite{IEEEexample:zhao2011comparing}
to result the word weight distribution of blog $b$.
Unlike TF-IDF, Twitter-LDA first trains the overall blogs, allocating each blog with a \textit{tag}.
%
The structure of \textit{tag} is as follows:
\begin{equation}
\label{eq:tw-tag}
W_t = \{(w'_i, p'_i)\}
\end{equation}
where $w'_i$ refers to a word in \textit{tag} $W_t$, and $p'_i$ is the probability that $w'_i$ appears in blogs with the said \textit{tag}, with $\sum_{\substack{i}} p'_i = 1$ ($|W_t|\ =\ 30$ in this work by default).
%
Subsequently, $W_t$ are leveraged to conclude $W_w$, i.e., $W_w\ =\ W_t$ , which shares the format with that of $W_f$.
Go to \textbf{Step 6}.

@@

\stitle{Step 7:} Hence, the similarity of a blog $b$ against a lexicon topic $t$ is given by:
\begin{equation}
\label{eq:simbt}
sim(b, t) = \alpha * sim(W_f, t) + (1 - \alpha) * sim(W_t, t)
\end{equation}
where the $\alpha$ is a parameter by which \sys{} could set flexible priorities between TF-IDF and Twitter-LDA.
Go to \textbf{Step 8}.

\stitle{Step 8:} Repeat the above steps (Step 1 to Step 7) for the blog $b$ over every topic in lexicon, i.e., $\forall t_k \in L$ results one similarity value of $sim(b, t_k)$.
Such computation further extends to all the blogs owned by user $u$, such that:
$\forall b_m \in B_s(u)$, $\forall t_k \in L$, there exists a similarity of $sim(b_m, t_k)$.
Hence, the overall similarity of user $u$ over lexicon topics $\{t\}$ (i.e., $L$), written as $S(u,\ L)$, could be denoted by a vector:
\begin{equation}
\label{eq:simul}
S(u, L) = (s_0,\ s_1,\ ...,\ s_{n-1})
\end{equation}
where $n$ refers to the cardinality of $L$ (i.e., number of topics in $L$) and $s_k$ is the overall similarity of user $u$ over topic $t_k$, which is given by:
\begin{equation}
\label{eq:simul-2}
s_k = \sum_{\substack{m}} sim(b_m, t_k)
\end{equation}

>>>>

With the underlying data in Data Storage subsystem, Feature Extraction is responsible for ``mining'' the user characteristics, resulting three features for each user.
These features are \textit{Info Feature}, \textit{Behavior Feature} and \textit{Interest Feature}, which constitute the \textit{Feature Data} in \sys{}, i.e., \textit{Feature Data} = \{\textit{Info Feature}, \textit{Behavior Feature}, \textit{Interest Feature}\}.

@@

\textit{Info Feature} employs a vector $I$ to cover the basic info of user.
\begin{equation}
\label{eq:info}
	I = (\#R_s,\ \#E_s,\ R_{ee},\ \#B_s,\ R_{oc},\ U_t)
\end{equation}
where each variable is illustrated in Table \ref{tbl:fe-info}.
Specifically, we use $\#(B_s | R(B)==1)$ and $\#(B_s | R(B)==0)$ to represent the number of \retd{} microblogs and microblogs that are originally created by the user.

\begin{table}[!htb]
\centering
\begin{small}
\caption{Illustration of Variables in Info Feature}
\vspace{0.3cm}
\label{tbl:fe-info}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{c}{\textbf{variable}} & \multicolumn{1}{c}{\textbf{illustration}}	\\	\midrule \midrule
\#$R_s$				& number of followers				\\	\midrule
\#$E_s$				& number of followees				\\	\midrule
\multirow{2}{*}{$R_{ee}$}      & \multirow{2}{*}{a ratio defined as $\frac{\#R_s}{\#E_s}$}	\\
 						&                       									\\	\midrule
\#$B_s$				& number of microblogs owned by the user				\\	\midrule
\multirow{2}{*}{$R_{oc}$}      & \multirow{2}{*}{a ratio defined as $\frac{\#(B_s | R(B)==1)}{\#(B_s | R(B)==0)}$}	\\
 						&                       									\\	\midrule
$U_t$					& user type (as detailed in Table \ref{tbl:ucate})			\\ \bottomrule
\end{tabular}
\end{small}
\end{table}

@@

Unlike \textit{Info Feature}, \textit{Behavior Feature} shows several statistics regarding the user's \retg{} behavior.
Such statistics include:
\begin{itemize}
	\item a value showing the average number of \retd{} microblogs per week: $\#W_r$
	\item a normalized vector regarding the time distribution of a user's \retg{} behavior: $P_t\ = (p'_0,\ p'_1,\ ...,\ p'_{11})$, where $p'_0$ is the probability that the \retg{} activity happens from 0am to 2am, $p'_1$ is the probability that the \retg{} activity happens from 2am to 4am, and so on.
	\item a normalized vector with respect to the gap distribution of a user's \retg{} behavior: $P_g\ = (p''_0,\ p''_1,\ ...,\ p''_{5})$, in which $p''_0$ is the probability that the gap between two \retd{} microblogs is within 1 min. Ditto for $p''_1$ (1 min to 1 hour), $p''_2$ (1 to 12 hours), $p''_3$ (12 to 24 hours), $p''_4$ (24 to 48 hours) and  $p''_5$ (more than 48 hours).
\end{itemize}

@@

\begin{definition}
\label{def:bw}
%used \label{def:blog} previously
With a given user $u$, each microblog $b \in B_s(u)$ could be decomposed into a set of words $\{w\}$, i.e., $b = \{w\}$.
\end{definition}

@@

In \sys{}, a word, either in the form of $c$ or $w$, acts as the minimum unit for analysis.
Hence, the similarity of a word pair ($w$, $c$), i.e., $sim(w, c)$, could be generalized to the similarity of a microblog against one topic $sim(b, t)$, and finally to a user versus each topic in lexicon $sim(u, \{t\})$; topics with similarity satisfying certain thresholds are allocated to the user $u$ and constitute the interests of $u$.

@@

\stitle{Step 1:} Each microblog of $u$ is decomposed into a word set, i.e., $b = \{w\}$ where $b \in B_s(u)$.

@@

If $sim(b, t)$ satisfies a certain threshold (3 by default) , topic $t$ is labeled to microblog $b$;
the user $u$ is then discovered having an explicit interest (topic) $t$.
Thus, by looking into the similarity of $b$ against all topics in lexicon, the explicit interests of $u$ is returned, in the form of interest feature (see Definition \ref{def:inte}).

@@

\stitle{Step 3:} A metric \textit{TF-IDF weight} $W_f$ is computed, i.e., employing TF-IDF (term-frequency and inverse document-frequency) to calculate the weight distribution of words in microblog $b$:
\begin{equation}
\label{eq:tf}
W_f = \{(w_i, p_i)\}
\end{equation}
where $w_i$ refers to a single word, of which the weight is $p_i$, with $\sum_{\substack{i}} p_i = 1$.

To compute such weight $p_i$ for word $w_i$, a metric $p''_i$ is first calculated as:
\begin{equation}
\label{eq:tf-w}
p''_i = \frac{|b_i|}{|b|} * log(\frac{|D_i|}{|D|})
\end{equation}
in which we use the operator $|\ |$ to measure the cardinality, such that $|b_i|$ is the occurrences of word $w_i$ in microblog $b$ and $|b|$ the total occurrences of all words in $b$.
Ditto for $|D_i|$ and $|D|$, except that the scope is the overall dataset, rather than a single microblog $b$.

@@

\stitle{Step 4:} Similarly, another metric \textit{Twitter-LDA weight} $W_w$ is obtained, i.e., using Twitter-LDA  %\ref{IEEEexample:zhao2011comparing}
\cite{IEEEexample:zhao2011comparing}
to result the word weight distribution of microblog $b$.
Unlike TF-IDF, Twitter-LDA first trains the overall microblogs, allocating each microblog with a \textit{tag}.
%
The structure of \textit{tag} is as follows:
\begin{equation}
\label{eq:tw-tag}
W_t = \{(w'_i, p'_i)\}
\end{equation}
where $w'_i$ refers to a word in \textit{tag} $W_t$, and $p'_i$ is the probability that $w'_i$ appears in microblogs with the said \textit{tag}, with $\sum_{\substack{i}} p'_i = 1$ ($|W_t|\ =\ 30$ in this work by default).
%
Subsequently, $W_t$ are leveraged to conclude $W_w$, i.e., $W_w\ =\ W_t$ , which shares the format with that of $W_f$.
Go to \textbf{Step 6}.

@@

\stitle{Step 7:} Hence, the similarity of a microblog $b$ against a lexicon topic $t$ is given by:
\begin{equation}
\label{eq:simbt}
sim(b, t) = \alpha * sim(W_f, t) + (1 - \alpha) * sim(W_t, t)
\end{equation}
where the $\alpha$ is a parameter by which \sys{} could set flexible priorities between TF-IDF and Twitter-LDA.
Go to \textbf{Step 8}.

\stitle{Step 8:} Repeat the above steps (Step 1 to Step 7) for the microblog $b$ over every topic in lexicon, i.e., $\forall t_k \in L$ results one similarity value of $sim(b, t_k)$.
Such computation further extends to all the microblogs owned by user $u$, such that:
$\forall b_m \in B_s(u)$, $\forall t_k \in L$, there exists a similarity of $sim(b_m, t_k)$.
Hence, the overall similarity of user $u$ over lexicon topics $\{t\}$ (i.e., $L$), written as $S(u,\ L)$, could be denoted by a vector:
\begin{equation}
\label{eq:simul}
S(u, L) = (s_0,\ s_1,\ ...,\ s_{n-1})
\end{equation}
where $n$ refers to the cardinality of $L$ (i.e., number of topics in $L$) and $s_k$ is the overall similarity of user $u$ over topic $t_k$, which is given by:
\begin{equation}
\label{eq:simul-2}
s_k = \sum_{\substack{m}} sim(b_m, t_k)
\end{equation}

### 2017-10-11 Gruba/04-uc.tex
v4.2
v4.2

Providing the \textit{Feature Data}, User Clusterer takes the charge of grouping each user concerned into a proper cluster.
Algorithm \ref{alg:uc} illustrates such overall procedure.
%
The idea is to enumerate a number of clustering trials (line \ref{enu}) and select the optimal solution with the best Silhouette coefficient value ($v$ in line \ref{opti}).
In principle, each trial (referred by $t$ in line \ref{enu}) first performs a clustering task (line \ref{task}; to be detailed in section \ref{sec:cluster}), resulting a cluster (by $l(u)$) for each user $u$ (line \ref{l});
then, each user obtains a Silhouette coefficient value $v(u)$ stemmed from the in/out-cluster distances (lines \ref{v-b}--\ref{v-e}; shall be illustrated in section \ref{sec:compu});
finally, the averaged Silhouette coefficient value of all users serves as the Silhouette coefficient value of the current trial, written as $v(t)$ (line \ref{avg}), by which the said selection process is conducted (line \ref{opti}).

@@

Unlike K-Prototype that supports vector samples in which each dimension is of numerical/categorical, K-Gru could also handle the case where a dimension is one normalized vector.
%
Recall the sample data for User Clusterer, i.e., \textit{Feature Data} in form of vectors (see formula \ref{eq:fu-flat}), of which the data type regarding each dimension is shown as Table \ref{tbl:data-type}.

>>>>

Providing the \textit{Feature Data}, User Clustering takes the charge of grouping each user concerned into a proper cluster.
Algorithm \ref{alg:uc} illustrates such overall procedure.
%
The idea is to enumerate a number of clustering trials (line \ref{enu}) and select the optimal solution with the best Silhouette coefficient value ($v$ in line \ref{opti}).
In principle, each trial (referred by $t$ in line \ref{enu}) first performs a clustering task (line \ref{task}; to be detailed in section \ref{sec:cluster}), resulting a cluster (by $l(u)$) for each user $u$ (line \ref{l});
then, each user obtains a Silhouette coefficient value $v(u)$ stemmed from the in/out-cluster distances (lines \ref{v-b}--\ref{v-e}; shall be illustrated in section \ref{sec:compu});
finally, the averaged Silhouette coefficient value of all users serves as the Silhouette coefficient value of the current trial, written as $v(t)$ (line \ref{avg}), by which the said selection process is conducted (line \ref{opti}).

@@

Unlike K-Prototype that supports vector samples in which each dimension is of numerical/categorical, K-Gru could also handle the case where a dimension is one normalized vector.
%
Recall the sample data for User Clustering, i.e., \textit{Feature Data} in form of vectors (see formula \ref{eq:fu-flat}), of which the data type regarding each dimension is shown as Table \ref{tbl:data-type}.

### 2017-10-11 Gruba/05-gm.tex
v4.2
v4.2

\section{Group based Behavior Modelling}
\label{sec:gm}

@@

Recall the central problem of \sys{}, where the \retg{} behaviors of users are modeled.
Specifically, such model is built by Group Modeler for each user group and thus named as group model.
To avoid ambiguity, we shall use the term of \textit{items} to denote the data for training the group model.
A given \textit{item} is either positive or negative.

\begin{definition}
\label{def:gm-it}
An item $E$ involves a blog $b$ and a user $f$ such that $f\ \in R_s(O(b))$, i.e., $f$ is a follower of  the owner of blog $b$.
\begin{equation}
\label{eq:gm-it}
E \in
  \begin{cases}
    \text{positive items}       & \quad \text{if } f \text{ \retd{} } b\\
    \text{negative items}  		& \quad \text{if } f \text{ did not \ret{} } b
  \end{cases}
\end{equation}
\end{definition}

@@

	\stab(2) \stitle{Blog Info} considers the correlation between blog contents and recent events, where the latter is returned by Ring \cite{IEEEexample:ring}. The correlation metric $C_h$ is in the form of a normalized vector with each dimension represents one event (similar as $P_f$ in formula \ref{eq:inte}). Each event could be viewed as a topic $t$, over which the correlation of a blog $b$ could be obtained by formula \ref{eq:simbt}.

	\stab(3) \stitle{Interaction Info} includes three correlation metrics. They are of blog $b$ versus the user $u$'s \textit{Interest Feature} $P_f(u)$ (a.k.a. long-term/stable interest in this work), $b$ versus $u$'s short-term interest $P_s(u)$ that is mined from $u$'s recent blogs (e.g., within 30 days) in the same manner of $P_f(u)$, and $b$'s timestamp versus the time distribution of $u$'s \retg{} behavior $P_t$.
%\end{itemize}
In this paper, we see modeling retweeting behavior of group as a classification problem and use random forest classifier to solve the problem. The advantage of using classification model is that we can integrate different combinations of the features into the model conveniently. As a result, the obtained group behavior model could learn what does a positive/negative item look like over each metric mentioned above.\par

>>>>

\section{Group based Behavior Modeling}
\label{sec:gm}

@@

Recall the central problem of \sys{}, where the \retg{} behaviors of users are modeled.
Specifically, such model is built by Group Modeling for each user group and thus named as group model.
To avoid ambiguity, we shall use the term of \textit{items} to denote the data for training the group model.
A given \textit{item} is either positive or negative.

\begin{definition}
\label{def:gm-it}
An item $E$ involves a microblog $b$ and a user $f$ such that $f\ \in R_s(O(b))$, i.e., $f$ is a follower of  the owner of microblog $b$.
\begin{equation}
\label{eq:gm-it}
E \in
  \begin{cases}
    \text{positive items}       & \quad \text{if } f \text{ \retd{} } b\\
    \text{negative items}  		& \quad \text{if } f \text{ did not \ret{} } b
  \end{cases}
\end{equation}
\end{definition}

@@

	\stab(2) \stitle{Microblog Info} considers the correlation between microblog contents and recent events, where the latter is returned by Ring \cite{IEEEexample:ring}. The correlation metric $C_h$ is in the form of a normalized vector with each dimension represents one event (similar as $P_f$ in formula \ref{eq:inte}). Each event could be viewed as a topic $t$, over which the correlation of a microblog $b$ could be obtained by formula \ref{eq:simbt}.

	\stab(3) \stitle{Interaction Info} includes three correlation metrics. They are of microblog $b$ versus the user $u$'s \textit{Interest Feature} $P_f(u)$ (a.k.a. long-term/stable interest in this work), $b$ versus $u$'s short-term interest $P_s(u)$ that is mined from $u$'s recent microblogs (e.g., within 30 days) in the same manner of $P_f(u)$, and $b$'s timestamp versus the time distribution of $u$'s \retg{} behavior $P_t$.
%\end{itemize}
In this paper, we see modeling retweeting behavior of group as a classification problem and use random forest classifier to solve the problem. The advantage of using classification model is that we can integrate different combinations of the features into the model conveniently. As a result, the obtained group behavior model could learn what does a positive/negative item look like over each metric mentioned above.\par
